Type Error Telemetry at Scale: Pseudonymized and Stochiastic

### 2023-09-18 programming23/paper.tex
checkpoint: te edit range

At a higher level, this paper is the first to use telemetry 
to study a typechecker.
It thus represents a step toward data-driven language design,
informed by many users' actual practice.
Our data captures over 340,000 sessions
that occured between February and April 2023
and includes 72 million type analysis errors.
By contrast to typical qualitative methods (e.g., surveys and interviews), it
is not restricted to users' \emph{perceptions} about their work and it is not
limited to a small number of users.

@@

In order to avoid swamping our telemetry servers, we randomly throttle
the generation of telemetry records:
\begin{itemize}
  \item
    1\% of Roblox Studio sessions were enrolled in generating telemetry, and
  \item
    0.5\% of runs of the typechecker (approximately 1 in 200 keystrokes)
      in an enrolled session generated a telemetry record.
\end{itemize}
In order to find how file-switching correlated with type errors, we additionally have:
\begin{itemize}
  \item
    every run of the typechecker in an enrolled session which switched file generated a telemetry record.
\end{itemize}
Each telemetry record contains:
\begin{description}
  \item[D1] metadata: a psedonymized session identifier, timestamp and session duration,
  \item[D2] mode of the current file: (\mnocheck{}, \mnonstrict{}, or \mstrict{}),
  \item[D3] reason for sending: (random selection, or file switch),
  \item[D4] size of codebase: number of files, and number of lines of code type checked,
  \item[D5] size of edit range
  \item[D6] overall type errors: for previous and current states, we have the total number, the nunber in the current file, and number in the edit range,
  \item[D7] specific errors in the edit range: for the previous and current states, for each type error code, the number type errors in the edit range,
  \item[D8] forced strict errors: specific errors for the
    edit range computed as if the user had strict mode enabled.
  \item[D9] TooComplexErrors: project-wide count for this one specific error type
\end{description}
To track the edit range, we record a start and end position, which we
update appropriately on every edit. This can result in very large edit
ranges, for example, if the user edits at the beginning and end of the
file.
The main benefit of this strategy is that it ensures constant-size telemetry records.

@@

\Cref{f:records-per-hour} provides a time-ordered distribution of the data.
Each vertical bar counts the number of records generated per hour according to
a client-side timestamp.
The bars are labeled with a California time zone because that is the locale of
the Roblox servers, which parsed the timestamps.
Most buckets contain roughly one thousand records, but some have very few
and a handful of others exceed three thousand.
%% \FILL{} investigate one tower, what's happening?? all one session?
There is a sharp drop in early April because we disabled telemetry at that point
but some clients continued to generate data
(\FILL{} Q. Alan, is that an ok sentence? I'm not sure why there's a long tail,
guess it could be people not updating studio or people with strange time settings
on their machine.)
We do not know which timezone the records originated in, but since the counts
tend to peak midday California time it seems that the majority
of Roblox developers are following a USA schedule (or rather, a Western
Hemisphere schedule).
The counts for weekends (shaded regions) are often the tallest; these days presumably
have a larger number of sessions for telemetry to observe.

@@

First, some records have odd timestamps according to the server's records.
Every telemetry record comes with two timestamps: a client-side timestamp
from when Roblox Studio created it and a server-side timestamp from when
the server posted it to its database.
The server timestamps are little use for our analysis because they bunch
together; it is common for several records to have identical server
timestamps.
However, server timestamps are useful for auditing because they should
be relatively close in value to the client timestamps.
For some records (<100? \FILL{}), though, the client is off by a large
margin: up to one week behind and up to one day ahead of the server.
We attribute the large delays to issues when sending telemetry (lost internet
connection, etc.) and smaller offsets to incorrect time settings on the client
machine.
In any event, we do not filter these records from further analysis.

@@

%% out/negative-edit-range.txt
%% actual value is NOT negative, but large positive over 4 billion
%% example: 4294967293
Third, the edit ranges are negative in a few hundred records~(1,533).
This is likely due to the user deleting a large block of code.
Since the issue affects so few records, we omit the negative ranges
from analysis (but, we do use other parts of the records; for example
the timestamps influence~\cref{f:records-per-hour}).
(\FILL{} Alan, double-check reasoning)

@@

There is a huge amount of variation across projects.
The largest ones have over 50k files (!) and 50k lines of code, and
there are many small ones with 1 file and/or 1 line of code.
Unsurprisingly, the numbers come with large standard deviations.
The median values are more reasonable, with roughly 3,000 lines of code
and 1,000 lines in edit ranges, but still have a large number of files: over 7,000.
The high number of files may be because creators define mavy components to
build a Roblox experience and put these components in separate files.
(\FILL{} still that's a lot of components ... any better guesses?)

@@

These adoption numbers are concerning.
Creators either do not know about type analysis, or they choose not
to use it in the code they are currently maintaining.
Uncovering the reason for low adaption is an important topic for future work on
Luau that has implications for the gradual typing community~(\cref{s:discussion}).

%% mostly pure, rare mixes
Most sessions (\pct{99.82}) stick to a single analysis mode.
These sessions never change the mode in the current module and never switch
focus to a module with a different analysis mode.
Among the other sessions, most (\pct{80}) switch to modules with
a different mode, about half contain at least one edit that upgrades the
current mode, and about half contain a downgrade.
There are 619 upgrades in total and 583 downgrades.
\FILL{} Ben check how often the downgrades follow the upgrades.

@@

The data does not support this explanation.
On average, the mode-upgrades in the data resulted in 3 additional
type errors (stddev 7, median 0).
The worst-case increase was 57 type errors, which is very high
but exceptional.
In another exception, upgrading modes removed three type errors
(presumably due to the increased precision of \mstrict{} mode
\FILL{} Alan, sounds plausible?).

@@

\subsection{Type Errors in Edit Range}
\label{s:type-error-count}

@@

    \begin{tabular}{lr@{}r@{}rr@{}r@{}rr@{}r@{}r}
      & \zerowidth{\mnocheck{}} & & & \zerowidth{\mnonstrict{}} & & & \zerowidth{\mstrict{}} & & \\
      & \rbox{Add} & \ybox{Keep} & \gbox{Drop} & \rbox{Add} & \ybox{Keep} & \gbox{Drop} & \rbox{Add} & \ybox{Keep} & \gbox{Drop} \\\midrule
      TypeMismatch & {0} & {0} & {0} & {159} & {62} & {129} & {21} & {10} & {28} \\
      UnknownSymbol & {0} & {0} & {0} & {2348} & {496} & {2973} & {49} & {19} & {55} \\
      UnknownProperty & {0} & {0} & {0} & {347} & {180} & {385} & {19} & {19} & {35} \\
      NotATable & {0} & {0} & {0} & {7} & {2} & {8} & {2} & {0} & {1} \\
      CannotExtendTable & {0} & {0} & {0} & {7} & {9} & {10} & {0} & {0} & {1} \\
      OnlyTablesCanHaveMethods & {0} & {0} & {0} & {1} & {0} & {2} & {0} & {0} & {0} \\
      DuplicateTypeDefinition & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {0} \\
      CountMismatch & {0} & {0} & {0} & {223} & {48} & {269} & {12} & {2} & {17} \\
      FunctionDoesNotTakeSelf & {0} & {0} & {0} & {4} & {6} & {5} & {0} & {0} & {0} \\
      OccursCheckFailed & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {1} \\
      UnknownRequire & {0} & {0} & {0} & {91} & {39} & {85} & {12} & {3} & {4} \\
      IncorrectGenericParameterCount & {0} & {0} & {0} & {0} & {0} & {0} & {1} & {0} & {1} \\
      SyntaxError & {8349} & {314} & {19220} & {983} & {46} & {2658} & {16} & {0} & {71} \\
      UnknownPropButFoundLikeProp & {0} & {0} & {0} & {26} & {18} & {21} & {1} & {0} & {1} \\
      GenericError & {0} & {0} & {0} & {206} & {52} & {203} & {8} & {1} & {9} \\
      CannotCallNonFunction & {0} & {0} & {0} & {17} & {4} & {20} & {1} & {0} & {1} \\
      ExtraInformation & {0} & {0} & {0} & {48} & {7} & {39} & {2} & {0} & {1} \\
      ModuleHasCyclicDependency & {0} & {0} & {0} & {20} & {9} & {15} & {0} & {0} & {1} \\
      IllegalRequire & {0} & {0} & {0} & {16} & {3} & {33} & {0} & {0} & {2} \\
      FunctionExitsWithoutReturning & {0} & {0} & {0} & {9} & {3} & {6} & {11} & {5} & {8} \\
      CannotInferBinaryOperation & {0} & {0} & {0} & {1} & {2} & {1} & {7} & {6} & {9} \\
      MissingProperties & {0} & {0} & {0} & {11} & {3} & {11} & {6} & {4} & {6} \\
      OptionalValueAccess & {0} & {0} & {0} & {40} & {52} & {27} & {6} & {2} & {7} \\
      MissingUnionProperty & {0} & {0} & {0} & {1} & {0} & {2} & {0} & {0} & {0} \\
      TypesAreUnrelated & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {1} \\
    \end{tabular}

@@

@@

FILL specific type errors, 1st add/drop, 2nd popularity

FILL type error counts
Mostly syntax errors though!
Estimate \pct{40} are substantial type errors rather than syntax
errors based on the edit range type errors~(\cref{s:type-error-count})
but unfortunately we cannot get an exact number for the overall
or per-module type error counts.

FILL popularity over all old and new in edit range.
Syntax error by far the most common.
UnknownSymbol is likely a syntax error --- so \pct{90} syntax error!

TODO get counts for each mode. Are there fewer stx errors in strict mode??!

NOTE can't ask about type errors at end because we don't know
the end.
The final record can be sent minutes before the end of session.

\begin{table}[t]\centering
  %% NOTE: popularity looks similar when [over all records] vs. [restricted to module switch records]

  \begin{tabular}{ll}
    \mnonstrict{} & \mstrict{} \\
    \begin{tabular}[t]{l@{~}r}
      \code{UnknownSymbol} & \pct{62.13} \\
      \code{SyntaxError} & \pct{15.42} \\
      \code{UnknownProperty} & \pct{8.28} \\
      \code{UnknownRequire} & \pct{3.13} \\
      \code{TypeMismatch} & \pct{2.44} \\
      \code{CountMismatch} & \pct{2.26} \\
      \code{OptionalValueAccess} & \pct{2.07} \\
      \code{GenericError} & \pct{2.06} \\
      \code{UnknownPropButFoundLikeProp} & \pct{0.44} \\
      \code{CannotExtendTable} & \pct{0.42} \\
      \code{ExtraInformation} & \pct{0.32} \\
      \code{ModuleHasCyclicDependency} & \pct{0.23} \\
      \code{IllegalRequire} & \pct{0.20} \\
      \code{NotATable} & \pct{0.15} \\
      \code{CannotCallNonFunction} & \pct{0.15} \\
      \code{MissingProperties} & \pct{0.09} \\
      \code{FunctionExitsWithoutReturning} & \pct{0.07} \\
      \code{FunctionDoesNotTakeSelf} & \pct{0.07} \\
      \code{MissingUnionProperty} & \pct{0.02} \\
      \code{CannotInferBinaryOperation} & \pct{0.02} \\
      \code{OnlyTablesCanHaveMethods} & \pct{0.01} \\
      \code{DuplicateTypeDefinition} & {<\pct{0.01}} \\
      \code{TypesAreUnrelated} & {<\pct{0.01}} \\
    \end{tabular}
        &
    \begin{tabular}[t]{l@{~}r}
      \code{UnknownSymbol} & \pct{23.97} \\
      \code{TypeMismatch} & \pct{20.46} \\
      \code{UnknownProperty} & \pct{18.88} \\
      \code{SyntaxError} & \pct{9.31} \\
      \code{CannotInferBinaryOperation} & \pct{6.94} \\
      \code{MissingProperties} & \pct{4.04} \\
      \code{CountMismatch} & \pct{2.99} \\
      \code{OptionalValueAccess} & \pct{2.99} \\
      \code{FunctionExitsWithoutReturning} & \pct{2.99} \\
      \code{UnknownRequire} & \pct{2.37} \\
      \code{GenericError} & \pct{2.28} \\
      \code{NotATable} & \pct{1.32} \\
      \code{ExtraInformation} & \pct{0.35} \\
      \code{UnknownPropButFoundLikeProp} & \pct{0.26} \\
      \code{IncorrectGenericParameterCount} & \pct{0.18} \\
      \code{CannotCallNonFunction} & \pct{0.18} \\
      \code{IllegalRequire} & \pct{0.18} \\
      \code{ModuleHasCyclicDependency} & \pct{0.09} \\
      \code{CannotExtendTable} & \pct{0.09} \\
      \code{OccursCheckFailed} & \pct{0.09} \\
      \code{TypesAreUnrelated} & \pct{0.09} \\
    \end{tabular}
  \end{tabular}

  \caption{Type error popularity for \mnonstrict{} and \mstrict{} modes.
  In \mnocheck{}, \code{SyntaxError} accounts for \pct{100} of the error.}
  \label{t:type-error-count}
\end{table}

\section{Analysis}

>>>>

At a higher level, this paper is the first to use telemetry 
to study a typechecker.
It thus represents a step toward data-driven language design,
informed by many users' actual practice.
Our data captures over 340,000 sessions
that occured between February and April 2023
and includes 72 million type analysis errors.
By contrast to typical qualitative methods such as surveys and interviews, it
is not restricted to users' \emph{perceptions} about their work and it is not
limited to a small number of users.

@@

In order to avoid swamping our telemetry servers, we randomly throttle
the generation of telemetry records:
\begin{itemize}
  \item
    1\% of Roblox Studio sessions were enrolled in generating telemetry, and
  \item
    0.5\% of runs of the typechecker (approximately 1 in 200 keystrokes)
      in an enrolled session generated a telemetry record.
\end{itemize}
In order to find how file-switching correlated with type errors, we additionally have:
\begin{itemize}
  \item
    every run of the typechecker in an enrolled session which switched file generated a telemetry record.
\end{itemize}
Each telemetry record contains:
\begin{description}
  \item[D1] metadata: a psedonymized session identifier, timestamp and session duration,
  \item[D2] mode of the current file: (\mnocheck{}, \mnonstrict{}, or \mstrict{}),
  \item[D3] reason for sending: (random selection, or file switch),
  \item[D4] size of codebase: number of files, and number of lines of code type checked,
  \item[D5] size of edit range
  \item[D6] overall type errors: for previous and current states, we have the total number, the nunber in the current file, and number in the edit range,
  \item[D7] specific errors in the edit range: for the previous and current states, for each type error code, the number type errors in the edit range,
    \FILL{} explain previous/current in detail, explain that this data takes up most of the telemetry record
  \item[D8] forced strict errors: specific errors for the
    edit range computed as if the user had strict mode enabled.
  \item[D9] TooComplexErrors: project-wide count for this one specific error type
\end{description}
To track the edit range, we record a start and end position, which we
update appropriately on every edit. This can result in very large edit
ranges, for example, if the user edits at the beginning and end of the
file.
The main benefit of this strategy is that it ensures constant-size telemetry records.

@@

\Cref{f:records-per-hour} provides a time-ordered distribution of the data.
Each vertical bar counts the number of records generated per hour according to
a client-side timestamp.
The bars are labeled with a California time zone because that is the locale of
the Roblox servers, which parsed the timestamps.
Most buckets contain roughly one thousand records, but some have very few
and a handful of others exceed three thousand.
%% \FILL{} investigate one tower, what's happening?? all one session?
There is a sharp drop in early April when the experiment was finished
and the telemetry probe was removed (though there is a long tail as
developers uopdated Roblox Studio).
We do not know which timezone the records originated in, but since the counts
tend to peak midday California time it seems that the majority
of Roblox developers are following a Western Hemisphere schedule.
The counts for weekends (shaded regions) are often the tallest,
as Roblox has a significant school-aged creator community.

@@

First, some records have odd timestamps according to the server's records.
Every telemetry record comes with two timestamps: a client-side timestamp
from when Roblox Studio created it and a server-side timestamp from when
the server posted it to its database.
The server timestamps are little use for our analysis because they bunch
together; it is common for several records to have identical server
timestamps.
However, server timestamps are useful for auditing because they should
be relatively close in value to the client timestamps.
For a small number of records (<100? \FILL{}), though, the client is off by a large
margin: up to one week behind and up to one day ahead of the server.
We attribute the large delays to issues when sending telemetry (lost internet
connection, etc.) and smaller offsets to incorrect time settings on the client
machine.
In any event, we do not filter these records from further analysis.

@@

%% out/negative-edit-range.txt
%% actual value is NOT negative, but large positive over 4 billion
%% example: 4294967293
Third, the edit ranges are negative in a few hundred records~(1,533).
This is likely due to the user deleting a large block of code.
Since the issue affects so few records, we omit the negative ranges
from analysis (but, we do use other parts of the records; for example
the timestamps influence~\cref{f:records-per-hour}).
%% (\FILL{} Alan, double-check reasoning)
%% Seems fine by me

@@

There is a huge amount of variation across projects.
The largest ones have over 50k files (!) and 50k lines of code, and %50kLoC and 50k files????
there are many small ones with 1 file and/or 1 line of code.
Unsurprisingly, the numbers come with large standard deviations.
The median values are more reasonable, with roughly 3,000 lines of code
and 1,000 lines in edit ranges, but still have a large number of files: over 7,000.
The high number of files may be because creators define many components to
build a Roblox experience and put these components in separate files.
(\FILL{} still that's a lot of components ... any better guesses?)

% That seems way off, not sure we're seeing so many files :/

@@

% I think this is too negative!
%% These adoption numbers are concerning.
%% Creators either do not know about type analysis, or they choose not
%% to use it in the code they are currently maintaining.
%% Uncovering the reason for low adaption is an important topic for future work on
%% Luau that has implications for the gradual typing community~(\cref{s:discussion}).

These adoption numbers indicate that there is a communication gap;
as long as type checking is opt-in, most developers stay opted out.
Once Luau type checking is opt-out rather than opt-in, it will be interesting
to revisit these numbers.

%% mostly pure, rare mixes
Most sessions (\pct{99.82}) stick to a single analysis mode.
These sessions never change the mode in the current module and never switch
focus to a module with a different analysis mode.
Among the mixed-mode sessions, most (\pct{80}) switch to modules with
a different mode, about half contain at least one edit that upgrades the
current mode, and about half contain a downgrade.
There are 619 upgrades in total and 583 downgrades.
\FILL{} Ben check how often the downgrades follow the upgrades.

@@

The data does not support this explanation.
On average, the mode-upgrades in the data resulted in 3 additional
type errors (stddev 7, median 0).
The worst-case increase was 57 type errors, which is very high
but exceptional.
In another exception, upgrading modes removed three type errors
% (presumably due to the increased precision of \mstrict{} mode
% \FILL{} Alan, sounds plausible?).
% My guess as to what;s going on
(possibly due to ther edits being rolled in with the
mode change).

@@

\subsection{Type Errors vs. Program Edits}
\label{s:type-error-survival}

Equipped with an overall picture of the dataset and the skewed usage
of \mnocheck{}, \mnonstrict{}, and \mstrict{} modes, we are ready to explore
the type error data.
Our main focus is on the intersection between type errors
and edits to the programs.
When a type error highlights part of the code and the next edit range includes
that code, we want to know whether the error survives the edit.
Similarly, we want to know when an edit introduces a type error.

\Cref{t:type-error-survival} counts the number of times that types
errors overlap with the current edit range.
There are three sets of columns, corresponding to the \mnocheck{},
\mnonstrict{}, and \mstrict{} type analysis modes.
Within each set, the Add columns counts the number of telemetry records
that introduce a certain type error.
For example, seventeen of the \mnonstrict{} records add
at least one \code{CannotCallNonFunction} error to the current edit range.
The Keep columns counts records that have the same, non-zero number of type errors
before and after.
Lastly, the Remove columns count records that decrease the number of type errors.

All three counts are imprecise because our telemetry does not track the exact
identity of a type error.
Suppose a creator removes one \code{CannotCallNonFunction} error but then
immediately introduces another on a different line.
\Cref{t:type-error-survival} reports this pair of edits as a Keep rather than
an Add and a Remove because we cannot distinguish two errors of the same kind.

\paragraph{Observations}

%% \paragraph{Most Type Errors are Typos}
One striking aspect of~\cref{t:type-error-survival} is the large number
of \code{SyntaxError}s and the related errors \code{UnknownSymbol} and
\code{UnknownProperty}.
Most type errors in the data are likely due to typos.
\Cref{s:type-error-count} discusses this point in detail.
For now, we remark that \code{SyntaxError} is the only possible error
in \mnocheck{} mode (by design) and observe that these errors are
usually in the Drop column and seldom in the Keep column.

A second observation is that there are relatively few errors that overlap
with the edit range; the numbers are low in general.
The highest value in the \mstrict{} columns is 71, meaning 71 records
drop a syntax error.
This number is very small relative to the total number of \mstrict{} records
from~\cref{f:dataset-overview} (6,505), and similarly for
the \mnonstrict{} and \mnocheck{} modes.
%% FILL show percentages for all three modes?
Edits seldom overlap with type errors.
\FILL{} what does this mean? Not sure if bad, or inconclusive.

When edits do overlap, however, ... good?

\paragraph{Do Error Highlights Help?}

\paragraph{Do Types Improve Quality of Life?}

%% use the ... percent of all records??
%% total 1.3M nocheck, 156K nonstrict, 6K strict
%% ... uhhh wow so few errors!

@@

    \begin{tabular}{lr@{}r@{}rr@{}r@{}rr@{}r@{}r}
      & \zerowidth{\mnocheck{}} & & & \zerowidth{\mnonstrict{}} & & & \zerowidth{\mstrict{}} & & \\
      & \rbox{Add} & \ybox{Keep} & \gbox{Drop} & \rbox{Add} & \ybox{Keep} & \gbox{Drop} & \rbox{Add} & \ybox{Keep} & \gbox{Drop} \\\midrule
      \code{CannotCallNonFunction} & {0} & {0} & {0} & {17} & {4} & {20} & {1} & {0} & {1} \\
      \code{CannotExtendTable} & {0} & {0} & {0} & {7} & {9} & {10} & {0} & {0} & {1} \\
      \code{CannotInferBinaryOperation} & {0} & {0} & {0} & {1} & {2} & {1} & {7} & {6} & {9} \\
      \code{CountMismatch} & {0} & {0} & {0} & {223} & {48} & {269} & {12} & {2} & {17} \\
      \code{DuplicateTypeDefinition} & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {0} \\
      \code{ExtraInformation} & {0} & {0} & {0} & {48} & {7} & {39} & {2} & {0} & {1} \\
      \code{FunctionDoesNotTakeSelf} & {0} & {0} & {0} & {4} & {6} & {5} & {0} & {0} & {0} \\
      \code{FunctionExitsWithoutReturning} & {0} & {0} & {0} & {9} & {3} & {6} & {11} & {5} & {8} \\
      \code{GenericError} & {0} & {0} & {0} & {206} & {52} & {203} & {8} & {1} & {9} \\
      \code{IllegalRequire} & {0} & {0} & {0} & {16} & {3} & {33} & {0} & {0} & {2} \\
      \code{IncorrectGenericParameterCount} & {0} & {0} & {0} & {0} & {0} & {0} & {1} & {0} & {1} \\
      \code{MissingProperties} & {0} & {0} & {0} & {11} & {3} & {11} & {6} & {4} & {6} \\
      \code{MissingUnionProperty} & {0} & {0} & {0} & {1} & {0} & {2} & {0} & {0} & {0} \\
      \code{ModuleHasCyclicDependency} & {0} & {0} & {0} & {20} & {9} & {15} & {0} & {0} & {1} \\
      \code{NotATable} & {0} & {0} & {0} & {7} & {2} & {8} & {2} & {0} & {1} \\
      \code{OccursCheckFailed} & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {1} \\
      \code{OnlyTablesCanHaveMethods} & {0} & {0} & {0} & {1} & {0} & {2} & {0} & {0} & {0} \\
      \code{OptionalValueAccess} & {0} & {0} & {0} & {40} & {52} & {27} & {6} & {2} & {7} \\
      \code{SyntaxError} & {8349} & {314} & {19220} & {983} & {46} & {2658} & {16} & {0} & {71} \\
      \code{TypeMismatch} & {0} & {0} & {0} & {159} & {62} & {129} & {21} & {10} & {28} \\
      \code{TypesAreUnrelated} & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {1} \\
      \code{UnknownPropButFoundLikeProp} & {0} & {0} & {0} & {26} & {18} & {21} & {1} & {0} & {1} \\
      \code{UnknownProperty} & {0} & {0} & {0} & {347} & {180} & {385} & {19} & {19} & {35} \\
      \code{UnknownRequire} & {0} & {0} & {0} & {91} & {39} & {85} & {12} & {3} & {4} \\
      \code{UnknownSymbol} & {0} & {0} & {0} & {2348} & {496} & {2973} & {49} & {19} & {55}
    \end{tabular}

@@

\subsection{Type Error Popularity}
\label{s:type-error-count}

FILL type error popularity
Mostly syntax errors though!
Estimate \pct{40} are substantial type errors rather than syntax
errors based on the edit range type errors~(\cref{s:type-error-count})
but unfortunately we cannot get an exact number for the overall
or per-module type error counts.

\begin{table}[t]\centering
  %% NOTE: popularity looks similar when [over all records] vs. [restricted to module switch records]
  \caption{Type error popularity for \mnonstrict{} and \mstrict{} modes.
    All of the type errors in \mnocheck{} mode are \code{SyntaxError}s.}
  \label{t:type-error-count}
  \begin{tabular}{ll}
    \mnonstrict{} & \mstrict{} \\
    \begin{tabular}[t]{l@{~}r}
      \code{UnknownSymbol} & \pct{62.13} \\
      \code{SyntaxError} & \pct{15.42} \\
      \code{UnknownProperty} & \pct{8.28} \\
      \code{UnknownRequire} & \pct{3.13} \\
      \code{TypeMismatch} & \pct{2.44} \\
      \code{CountMismatch} & \pct{2.26} \\
      \code{OptionalValueAccess} & \pct{2.07} \\
      \code{GenericError} & \pct{2.06} \\
      \code{UnknownPropButFoundLikeProp} & \pct{0.44} \\
      \code{CannotExtendTable} & \pct{0.42} \\
      \code{ExtraInformation} & \pct{0.32} \\
      \code{ModuleHasCyclicDependency} & \pct{0.23} \\
      \code{IllegalRequire} & \pct{0.20} \\
      \code{NotATable} & \pct{0.15} \\
      \code{CannotCallNonFunction} & \pct{0.15} \\
      \code{MissingProperties} & \pct{0.09} \\
      \code{FunctionExitsWithoutReturning} & \pct{0.07} \\
      \code{FunctionDoesNotTakeSelf} & \pct{0.07} \\
      \code{MissingUnionProperty} & \pct{0.02} \\
      \code{CannotInferBinaryOperation} & \pct{0.02} \\
      \code{OnlyTablesCanHaveMethods} & \pct{0.01} \\
      \code{DuplicateTypeDefinition} & {<\pct{0.01}} \\
      \code{TypesAreUnrelated} & {<\pct{0.01}} \\
    \end{tabular}
        &
    \begin{tabular}[t]{l@{~}r}
      \code{UnknownSymbol} & \pct{23.97} \\
      \code{TypeMismatch} & \pct{20.46} \\
      \code{UnknownProperty} & \pct{18.88} \\
      \code{SyntaxError} & \pct{9.31} \\
      \code{CannotInferBinaryOperation} & \pct{6.94} \\
      \code{MissingProperties} & \pct{4.04} \\
      \code{CountMismatch} & \pct{2.99} \\
      \code{OptionalValueAccess} & \pct{2.99} \\
      \code{FunctionExitsWithoutReturning} & \pct{2.99} \\
      \code{UnknownRequire} & \pct{2.37} \\
      \code{GenericError} & \pct{2.28} \\
      \code{NotATable} & \pct{1.32} \\
      \code{ExtraInformation} & \pct{0.35} \\
      \code{UnknownPropButFoundLikeProp} & \pct{0.26} \\
      \code{IncorrectGenericParameterCount} & \pct{0.18} \\
      \code{CannotCallNonFunction} & \pct{0.18} \\
      \code{IllegalRequire} & \pct{0.18} \\
      \code{ModuleHasCyclicDependency} & \pct{0.09} \\
      \code{CannotExtendTable} & \pct{0.09} \\
      \code{OccursCheckFailed} & \pct{0.09} \\
      \code{TypesAreUnrelated} & \pct{0.09} \\
    \end{tabular}
  \end{tabular}
\end{table}

@@
